---
title: "IPEDS Data"
author: "Himanshi Manglunia, Kalpita Raut, Laura Walker"
date: "November 20, 2018"
output: html_document
---

```{r setup, include=FALSE}
# Load RODBC package 
# Connects R Code to the database/warehouse
# install.packages("RODBC") # only needs to be run once
library(RODBC)
library(rscorecard)
```
 ## Data from year 2015-16
```{r message=FALSE, cache=FALSE, echo=FALSE, warning=FALSE}

bigten <- data.frame(UNITID=c(151351, 171100, 147767, 204796, 214777, 243780, 186380, 145637, 153658, 163286, 170976, 174066, 181464, 240444), name=c('Indiana University', 'Michigan State University', 'Northwestern University', 'The Ohio State University', 'Penn State University', 'Purdue University', 'Rutgers University', 'University of Illinois at Urbana-Champaign', 'University of Iowa', 'University of Maryland', 'University of Michigan - Ann Arbor', 'University of Minnesota', 'University of Nebraska', 'University of Wisconsin'))
```

```{r message=FALSE, cache=FALSE, echo=FALSE, warning=FALSE}
library(readxl)
MERGED2016_17_PP <- read_excel("MERGED2016_17_PP.xlsx")
MERGED2016_17_PP <- merge(bigten, MERGED2016_17_PP, by.x="UNITID", by.y="UNITID", all.x = TRUE)
MERGED2016_17_PP$Year <- "2016-17"

MERGED2016_17_PP <- MERGED2016_17_PP[,c("UNITID", "name", "PCIP01", "PCIP03", "PCIP04", "PCIP05", "PCIP09", "PCIP10", "PCIP11", "PCIP12", "PCIP13", "PCIP14", "PCIP15", "PCIP16", "PCIP19", "PCIP22", "PCIP23", "PCIP24", "PCIP25", "PCIP26", "PCIP27", "PCIP29", "PCIP30", "PCIP31", "PCIP38", "PCIP39", "PCIP40", "PCIP41", "PCIP42", "PCIP43", "PCIP44", "PCIP45", "PCIP46", "PCIP47", "PCIP48", "PCIP49", "PCIP50", "PCIP51", "PCIP52", "PCIP54", "CIP01BACHL", "CIP03BACHL", "CIP04BACHL", "CIP05BACHL", "CIP09BACHL", "CIP10BACHL", "CIP11BACHL", "CIP12BACHL", "CIP13BACHL", "CIP14BACHL", "CIP15BACHL", "CIP16BACHL", "CIP19BACHL", "CIP22BACHL", "CIP23BACHL", "CIP24BACHL", "CIP25BACHL", "CIP26BACHL", "CIP27BACHL", "CIP29BACHL", "CIP30BACHL", "CIP31BACHL", "CIP38BACHL", "CIP39BACHL", "CIP40BACHL", "CIP41BACHL", "CIP42BACHL", "CIP43BACHL", "CIP44BACHL", "CIP45BACHL", "CIP46BACHL", "CIP47BACHL", "CIP48BACHL", "CIP49BACHL", "CIP50BACHL", "CIP51BACHL", "CIP52BACHL", "CIP54BACHL", "NPT4_PUB", "NPT41_PUB", "NPT42_PUB", "NPT43_PUB", "NPT44_PUB", "NPT45_PUB", "NPT4_048_PUB", "NPT4_3075_PUB", "NPT4_75UP_PUB", "NUM4_PUB", "NUM41_PUB", "NUM42_PUB", "NUM43_PUB", "NUM44_PUB", "NUM45_PUB", "PCTPELL", "C150_4", "D150_4", "C150_4_NRA", "PCTFLOAN", "COMPL_RPY_1YR_RT", "FEMALE_RPY_1YR_RT", "MALE_RPY_1YR_RT", "COMPL_RPY_3YR_RT", "FEMALE_RPY_3YR_RT", "MALE_RPY_3YR_RT", "COMPL_RPY_5YR_RT", "FEMALE_RPY_5YR_RT", "MALE_RPY_5YR_RT", "GRAD_DEBT_MDN", "WDRAW_DEBT_MDN", "LO_INC_DEBT_MDN", "MD_INC_DEBT_MDN", "HI_INC_DEBT_MDN", "DEP_DEBT_MDN", "IND_DEBT_MDN", "PELL_DEBT_MDN", "NOPELL_DEBT_MDN", "FEMALE_DEBT_MDN", "MALE_DEBT_MDN", "FIRSTGEN_DEBT_MDN", "NOTFIRSTGEN_DEBT_MDN", "DEBT_N", "GRAD_DEBT_N", "WDRAW_DEBT_N", "LO_INC_DEBT_N", "MD_INC_DEBT_N", "HI_INC_DEBT_N", "DEP_DEBT_N", "IND_DEBT_N", "PELL_DEBT_N", "NOPELL_DEBT_N", "FEMALE_DEBT_N", "MALE_DEBT_N", "FIRSTGEN_DEBT_N", "NOTFIRSTGEN_DEBT_N", "FEMALE_RPY_1YR_N", "MALE_RPY_1YR_N", "FEMALE_RPY_3YR_N", "MALE_RPY_3YR_N", "FEMALE_RPY_5YR_N", "MALE_RPY_5YR_N", "MN_EARN_WNE_INDEP0_P6", "MN_EARN_WNE_INDEP1_P6", "MN_EARN_WNE_MALE0_P6", "MN_EARN_WNE_MALE1_P6", "GRAD_DEBT_MDN_SUPP", "FEMALE_RPY_3YR_RT_SUPP", "MALE_RPY_3YR_RT_SUPP", "C100_4", "D150_4_WHITE", "D150_4_BLACK", "D150_4_HISP", "D150_4_ASIAN", "D150_4_AIAN", "D150_4_NHPI", "D150_4_2MOR", "D150_4_NRA", "D150_4_UNKN", "Year")]
```

```{r message=FALSE, cache=FALSE, echo=FALSE, warning=FALSE}
MERGED2015_16_PP <- read_excel("MERGED2015_16_PP.xlsx")
MERGED2015_16_PP <- merge(bigten, MERGED2015_16_PP, by.x="UNITID", by.y="UNITID", all.x = TRUE)
MERGED2015_16_PP$Year <- "2015-16"

MERGED2015_16_PP <- MERGED2015_16_PP[,c("UNITID", "name","PCIP01", "PCIP03", "PCIP04", "PCIP05", "PCIP09", "PCIP10", "PCIP11", "PCIP12", "PCIP13", "PCIP14", "PCIP15", "PCIP16", "PCIP19", "PCIP22", "PCIP23", "PCIP24", "PCIP25", "PCIP26", "PCIP27", "PCIP29", "PCIP30", "PCIP31", "PCIP38", "PCIP39", "PCIP40", "PCIP41", "PCIP42", "PCIP43", "PCIP44", "PCIP45", "PCIP46", "PCIP47", "PCIP48", "PCIP49", "PCIP50", "PCIP51", "PCIP52", "PCIP54", "CIP01BACHL", "CIP03BACHL", "CIP04BACHL", "CIP05BACHL", "CIP09BACHL", "CIP10BACHL", "CIP11BACHL", "CIP12BACHL", "CIP13BACHL", "CIP14BACHL", "CIP15BACHL", "CIP16BACHL", "CIP19BACHL", "CIP22BACHL", "CIP23BACHL", "CIP24BACHL", "CIP25BACHL", "CIP26BACHL", "CIP27BACHL", "CIP29BACHL", "CIP30BACHL", "CIP31BACHL", "CIP38BACHL", "CIP39BACHL", "CIP40BACHL", "CIP41BACHL", "CIP42BACHL", "CIP43BACHL", "CIP44BACHL", "CIP45BACHL", "CIP46BACHL", "CIP47BACHL", "CIP48BACHL", "CIP49BACHL", "CIP50BACHL", "CIP51BACHL", "CIP52BACHL", "CIP54BACHL", "NPT4_PUB", "NPT41_PUB", "NPT42_PUB", "NPT43_PUB", "NPT44_PUB", "NPT45_PUB", "NPT4_048_PUB", "NPT4_3075_PUB", "NPT4_75UP_PUB", "NUM4_PUB", "NUM41_PUB", "NUM42_PUB", "NUM43_PUB", "NUM44_PUB", "NUM45_PUB", "PCTPELL", "C150_4", "D150_4", "C150_4_NRA", "PCTFLOAN", "COMPL_RPY_1YR_RT", "FEMALE_RPY_1YR_RT", "MALE_RPY_1YR_RT", "COMPL_RPY_3YR_RT", "FEMALE_RPY_3YR_RT", "MALE_RPY_3YR_RT", "COMPL_RPY_5YR_RT", "FEMALE_RPY_5YR_RT", "MALE_RPY_5YR_RT", "GRAD_DEBT_MDN", "WDRAW_DEBT_MDN", "LO_INC_DEBT_MDN", "MD_INC_DEBT_MDN", "HI_INC_DEBT_MDN", "DEP_DEBT_MDN", "IND_DEBT_MDN", "PELL_DEBT_MDN", "NOPELL_DEBT_MDN", "FEMALE_DEBT_MDN", "MALE_DEBT_MDN", "FIRSTGEN_DEBT_MDN", "NOTFIRSTGEN_DEBT_MDN", "DEBT_N", "GRAD_DEBT_N", "WDRAW_DEBT_N", "LO_INC_DEBT_N", "MD_INC_DEBT_N", "HI_INC_DEBT_N", "DEP_DEBT_N", "IND_DEBT_N", "PELL_DEBT_N", "NOPELL_DEBT_N", "FEMALE_DEBT_N", "MALE_DEBT_N", "FIRSTGEN_DEBT_N", "NOTFIRSTGEN_DEBT_N", "FEMALE_RPY_1YR_N", "MALE_RPY_1YR_N", "FEMALE_RPY_3YR_N", "MALE_RPY_3YR_N", "FEMALE_RPY_5YR_N", "MALE_RPY_5YR_N", "MN_EARN_WNE_INDEP0_P6", "MN_EARN_WNE_INDEP1_P6", "MN_EARN_WNE_MALE0_P6", "MN_EARN_WNE_MALE1_P6", "GRAD_DEBT_MDN_SUPP", "FEMALE_RPY_3YR_RT_SUPP", "MALE_RPY_3YR_RT_SUPP", "C100_4", "D150_4_WHITE", "D150_4_BLACK", "D150_4_HISP", "D150_4_ASIAN", "D150_4_AIAN", "D150_4_NHPI", "D150_4_2MOR", "D150_4_NRA", "D150_4_UNKN", "Year")]
```

```{r message=FALSE, cache=FALSE, echo=FALSE, warning=FALSE}
MERGED2014_15_PP <- read_excel("MERGED2014_15_PP.xlsx")
MERGED2014_15_PP <- merge(bigten, MERGED2014_15_PP, by.x="UNITID", by.y="UNITID", all.x = TRUE)
MERGED2014_15_PP$Year <- "2014-15"

MERGED2014_15_PP <- MERGED2014_15_PP[,c("UNITID", "name","PCIP01", "PCIP03", "PCIP04", "PCIP05", "PCIP09", "PCIP10", "PCIP11", "PCIP12", "PCIP13", "PCIP14", "PCIP15", "PCIP16", "PCIP19", "PCIP22", "PCIP23", "PCIP24", "PCIP25", "PCIP26", "PCIP27", "PCIP29", "PCIP30", "PCIP31", "PCIP38", "PCIP39", "PCIP40", "PCIP41", "PCIP42", "PCIP43", "PCIP44", "PCIP45", "PCIP46", "PCIP47", "PCIP48", "PCIP49", "PCIP50", "PCIP51", "PCIP52", "PCIP54", "CIP01BACHL", "CIP03BACHL", "CIP04BACHL", "CIP05BACHL", "CIP09BACHL", "CIP10BACHL", "CIP11BACHL", "CIP12BACHL", "CIP13BACHL", "CIP14BACHL", "CIP15BACHL", "CIP16BACHL", "CIP19BACHL", "CIP22BACHL", "CIP23BACHL", "CIP24BACHL", "CIP25BACHL", "CIP26BACHL", "CIP27BACHL", "CIP29BACHL", "CIP30BACHL", "CIP31BACHL", "CIP38BACHL", "CIP39BACHL", "CIP40BACHL", "CIP41BACHL", "CIP42BACHL", "CIP43BACHL", "CIP44BACHL", "CIP45BACHL", "CIP46BACHL", "CIP47BACHL", "CIP48BACHL", "CIP49BACHL", "CIP50BACHL", "CIP51BACHL", "CIP52BACHL", "CIP54BACHL", "NPT4_PUB", "NPT41_PUB", "NPT42_PUB", "NPT43_PUB", "NPT44_PUB", "NPT45_PUB", "NPT4_048_PUB", "NPT4_3075_PUB", "NPT4_75UP_PUB", "NUM4_PUB", "NUM41_PUB", "NUM42_PUB", "NUM43_PUB", "NUM44_PUB", "NUM45_PUB", "PCTPELL", "C150_4", "D150_4", "C150_4_NRA", "PCTFLOAN", "COMPL_RPY_1YR_RT", "FEMALE_RPY_1YR_RT", "MALE_RPY_1YR_RT", "COMPL_RPY_3YR_RT", "FEMALE_RPY_3YR_RT", "MALE_RPY_3YR_RT", "COMPL_RPY_5YR_RT", "FEMALE_RPY_5YR_RT", "MALE_RPY_5YR_RT", "GRAD_DEBT_MDN", "WDRAW_DEBT_MDN", "LO_INC_DEBT_MDN", "MD_INC_DEBT_MDN", "HI_INC_DEBT_MDN", "DEP_DEBT_MDN", "IND_DEBT_MDN", "PELL_DEBT_MDN", "NOPELL_DEBT_MDN", "FEMALE_DEBT_MDN", "MALE_DEBT_MDN", "FIRSTGEN_DEBT_MDN", "NOTFIRSTGEN_DEBT_MDN", "DEBT_N", "GRAD_DEBT_N", "WDRAW_DEBT_N", "LO_INC_DEBT_N", "MD_INC_DEBT_N", "HI_INC_DEBT_N", "DEP_DEBT_N", "IND_DEBT_N", "PELL_DEBT_N", "NOPELL_DEBT_N", "FEMALE_DEBT_N", "MALE_DEBT_N", "FIRSTGEN_DEBT_N", "NOTFIRSTGEN_DEBT_N", "FEMALE_RPY_1YR_N", "MALE_RPY_1YR_N", "FEMALE_RPY_3YR_N", "MALE_RPY_3YR_N", "FEMALE_RPY_5YR_N", "MALE_RPY_5YR_N", "MN_EARN_WNE_INDEP0_P6", "MN_EARN_WNE_INDEP1_P6", "MN_EARN_WNE_MALE0_P6", "MN_EARN_WNE_MALE1_P6", "GRAD_DEBT_MDN_SUPP", "FEMALE_RPY_3YR_RT_SUPP", "MALE_RPY_3YR_RT_SUPP", "C100_4", "D150_4_WHITE", "D150_4_BLACK", "D150_4_HISP", "D150_4_ASIAN", "D150_4_AIAN", "D150_4_NHPI", "D150_4_2MOR", "D150_4_NRA", "D150_4_UNKN", "Year")]
```

```{r message=FALSE, cache=FALSE, echo=FALSE, warning=FALSE}
MERGED2013_14_PP <- read_excel("MERGED2013_14_PP.xlsx")
MERGED2013_14_PP <- merge(bigten, MERGED2013_14_PP, by.x="UNITID", by.y="UNITID", all.x = TRUE)
MERGED2013_14_PP$Year <- "2013-14"

MERGED2013_14_PP <- MERGED2013_14_PP[,c("UNITID", "name","PCIP01", "PCIP03", "PCIP04", "PCIP05", "PCIP09", "PCIP10", "PCIP11", "PCIP12", "PCIP13", "PCIP14", "PCIP15", "PCIP16", "PCIP19", "PCIP22", "PCIP23", "PCIP24", "PCIP25", "PCIP26", "PCIP27", "PCIP29", "PCIP30", "PCIP31", "PCIP38", "PCIP39", "PCIP40", "PCIP41", "PCIP42", "PCIP43", "PCIP44", "PCIP45", "PCIP46", "PCIP47", "PCIP48", "PCIP49", "PCIP50", "PCIP51", "PCIP52", "PCIP54", "CIP01BACHL", "CIP03BACHL", "CIP04BACHL", "CIP05BACHL", "CIP09BACHL", "CIP10BACHL", "CIP11BACHL", "CIP12BACHL", "CIP13BACHL", "CIP14BACHL", "CIP15BACHL", "CIP16BACHL", "CIP19BACHL", "CIP22BACHL", "CIP23BACHL", "CIP24BACHL", "CIP25BACHL", "CIP26BACHL", "CIP27BACHL", "CIP29BACHL", "CIP30BACHL", "CIP31BACHL", "CIP38BACHL", "CIP39BACHL", "CIP40BACHL", "CIP41BACHL", "CIP42BACHL", "CIP43BACHL", "CIP44BACHL", "CIP45BACHL", "CIP46BACHL", "CIP47BACHL", "CIP48BACHL", "CIP49BACHL", "CIP50BACHL", "CIP51BACHL", "CIP52BACHL", "CIP54BACHL", "NPT4_PUB", "NPT41_PUB", "NPT42_PUB", "NPT43_PUB", "NPT44_PUB", "NPT45_PUB", "NPT4_048_PUB", "NPT4_3075_PUB", "NPT4_75UP_PUB", "NUM4_PUB", "NUM41_PUB", "NUM42_PUB", "NUM43_PUB", "NUM44_PUB", "NUM45_PUB", "PCTPELL", "C150_4", "D150_4", "C150_4_NRA", "PCTFLOAN", "COMPL_RPY_1YR_RT", "FEMALE_RPY_1YR_RT", "MALE_RPY_1YR_RT", "COMPL_RPY_3YR_RT", "FEMALE_RPY_3YR_RT", "MALE_RPY_3YR_RT", "COMPL_RPY_5YR_RT", "FEMALE_RPY_5YR_RT", "MALE_RPY_5YR_RT", "GRAD_DEBT_MDN", "WDRAW_DEBT_MDN", "LO_INC_DEBT_MDN", "MD_INC_DEBT_MDN", "HI_INC_DEBT_MDN", "DEP_DEBT_MDN", "IND_DEBT_MDN", "PELL_DEBT_MDN", "NOPELL_DEBT_MDN", "FEMALE_DEBT_MDN", "MALE_DEBT_MDN", "FIRSTGEN_DEBT_MDN", "NOTFIRSTGEN_DEBT_MDN", "DEBT_N", "GRAD_DEBT_N", "WDRAW_DEBT_N", "LO_INC_DEBT_N", "MD_INC_DEBT_N", "HI_INC_DEBT_N", "DEP_DEBT_N", "IND_DEBT_N", "PELL_DEBT_N", "NOPELL_DEBT_N", "FEMALE_DEBT_N", "MALE_DEBT_N", "FIRSTGEN_DEBT_N", "NOTFIRSTGEN_DEBT_N", "FEMALE_RPY_1YR_N", "MALE_RPY_1YR_N", "FEMALE_RPY_3YR_N", "MALE_RPY_3YR_N", "FEMALE_RPY_5YR_N", "MALE_RPY_5YR_N", "MN_EARN_WNE_INDEP0_P6", "MN_EARN_WNE_INDEP1_P6", "MN_EARN_WNE_MALE0_P6", "MN_EARN_WNE_MALE1_P6", "GRAD_DEBT_MDN_SUPP", "FEMALE_RPY_3YR_RT_SUPP", "MALE_RPY_3YR_RT_SUPP", "C100_4", "D150_4_WHITE", "D150_4_BLACK", "D150_4_HISP", "D150_4_ASIAN", "D150_4_AIAN", "D150_4_NHPI", "D150_4_2MOR", "D150_4_NRA", "D150_4_UNKN", "Year")]
```

```{r message=FALSE, cache=FALSE, echo=FALSE, warning=FALSE}
MERGED2012_13_PP <- read_excel("MERGED2012_13_PP.xlsx")
MERGED2012_13_PP <- merge(bigten, MERGED2012_13_PP, by.x="UNITID", by.y="UNITID", all.x = TRUE)
MERGED2012_13_PP$Year <- "2012-13"

MERGED2012_13_PP <- MERGED2012_13_PP[,c("UNITID", "name","PCIP01", "PCIP03", "PCIP04", "PCIP05", "PCIP09", "PCIP10", "PCIP11", "PCIP12", "PCIP13", "PCIP14", "PCIP15", "PCIP16", "PCIP19", "PCIP22", "PCIP23", "PCIP24", "PCIP25", "PCIP26", "PCIP27", "PCIP29", "PCIP30", "PCIP31", "PCIP38", "PCIP39", "PCIP40", "PCIP41", "PCIP42", "PCIP43", "PCIP44", "PCIP45", "PCIP46", "PCIP47", "PCIP48", "PCIP49", "PCIP50", "PCIP51", "PCIP52", "PCIP54", "CIP01BACHL", "CIP03BACHL", "CIP04BACHL", "CIP05BACHL", "CIP09BACHL", "CIP10BACHL", "CIP11BACHL", "CIP12BACHL", "CIP13BACHL", "CIP14BACHL", "CIP15BACHL", "CIP16BACHL", "CIP19BACHL", "CIP22BACHL", "CIP23BACHL", "CIP24BACHL", "CIP25BACHL", "CIP26BACHL", "CIP27BACHL", "CIP29BACHL", "CIP30BACHL", "CIP31BACHL", "CIP38BACHL", "CIP39BACHL", "CIP40BACHL", "CIP41BACHL", "CIP42BACHL", "CIP43BACHL", "CIP44BACHL", "CIP45BACHL", "CIP46BACHL", "CIP47BACHL", "CIP48BACHL", "CIP49BACHL", "CIP50BACHL", "CIP51BACHL", "CIP52BACHL", "CIP54BACHL", "NPT4_PUB", "NPT41_PUB", "NPT42_PUB", "NPT43_PUB", "NPT44_PUB", "NPT45_PUB", "NPT4_048_PUB", "NPT4_3075_PUB", "NPT4_75UP_PUB", "NUM4_PUB", "NUM41_PUB", "NUM42_PUB", "NUM43_PUB", "NUM44_PUB", "NUM45_PUB", "PCTPELL", "C150_4", "D150_4", "C150_4_NRA", "PCTFLOAN", "COMPL_RPY_1YR_RT", "FEMALE_RPY_1YR_RT", "MALE_RPY_1YR_RT", "COMPL_RPY_3YR_RT", "FEMALE_RPY_3YR_RT", "MALE_RPY_3YR_RT", "COMPL_RPY_5YR_RT", "FEMALE_RPY_5YR_RT", "MALE_RPY_5YR_RT", "GRAD_DEBT_MDN", "WDRAW_DEBT_MDN", "LO_INC_DEBT_MDN", "MD_INC_DEBT_MDN", "HI_INC_DEBT_MDN", "DEP_DEBT_MDN", "IND_DEBT_MDN", "PELL_DEBT_MDN", "NOPELL_DEBT_MDN", "FEMALE_DEBT_MDN", "MALE_DEBT_MDN", "FIRSTGEN_DEBT_MDN", "NOTFIRSTGEN_DEBT_MDN", "DEBT_N", "GRAD_DEBT_N", "WDRAW_DEBT_N", "LO_INC_DEBT_N", "MD_INC_DEBT_N", "HI_INC_DEBT_N", "DEP_DEBT_N", "IND_DEBT_N", "PELL_DEBT_N", "NOPELL_DEBT_N", "FEMALE_DEBT_N", "MALE_DEBT_N", "FIRSTGEN_DEBT_N", "NOTFIRSTGEN_DEBT_N", "FEMALE_RPY_1YR_N", "MALE_RPY_1YR_N", "FEMALE_RPY_3YR_N", "MALE_RPY_3YR_N", "FEMALE_RPY_5YR_N", "MALE_RPY_5YR_N", "MN_EARN_WNE_INDEP0_P6", "MN_EARN_WNE_INDEP1_P6", "MN_EARN_WNE_MALE0_P6", "MN_EARN_WNE_MALE1_P6", "GRAD_DEBT_MDN_SUPP", "FEMALE_RPY_3YR_RT_SUPP", "MALE_RPY_3YR_RT_SUPP", "C100_4", "D150_4_WHITE", "D150_4_BLACK", "D150_4_HISP", "D150_4_ASIAN", "D150_4_AIAN", "D150_4_NHPI", "D150_4_2MOR", "D150_4_NRA", "D150_4_UNKN", "Year")]
```

```{r message=FALSE, cache=FALSE, echo=FALSE, warning=FALSE}
combined <- rbind(MERGED2016_17_PP, MERGED2015_16_PP, MERGED2014_15_PP, MERGED2013_14_PP, MERGED2012_13_PP)

 # Removes the individual years
rm(MERGED2016_17_PP, MERGED2015_16_PP, MERGED2014_15_PP, MERGED2013_14_PP, MERGED2012_13_PP)
# Counts the number of "n/a" exist in each column of the final data frame, IPEDS
combined_na_count <- sapply(combined, function(x) sum(is.na(x)))
combined_na_count <- as.data.frame.list(combined_na_count)
# Moves the data from wide to long:
library(reshape2)
combined_na_count <- melt(combined_na_count)
 # Writes a text file to working directory 
 write.table(combined,"combined_college_scorecards.txt",sep="\t",row.names=FALSE)
 ```
 ```{r message=FALSE, cache=FALSE, echo=FALSE, warning=FALSE}
 # Some Descriptive Analytics and a visualization by Laura Walker
 
college_scorecards <-read.csv(text=getURL("https://raw.githubusercontent.com/annlaurawalker/INFM_600/edits_descriptive/FinalDataset.csv"), header=T)

college_scorecards$group <- ifelse(college_scorecards$UNITID==163286, "MD", "Not MD")


md <- subset(college_scorecards, UNITID==163286)

md_repayment <- md[,c("Year", "DEP_DEBT_MDN", "FEMALE_DEBT_MDN", "GRAD_DEBT_MDN", "IND_DEBT_MDN", "MALE_DEBT_MDN", "MD_INC_DEBT_MDN", "NOPELL_DEBT_MDN", "NOTFIRSTGEN_DEBT_MDN", "PELL_DEBT_MDN", "WDRAW_DEBT_MDN")]

# wide to long
md_long <- gather(md_repayment, variable, md_value, DEP_DEBT_MDN:WDRAW_DEBT_MDN, factor_key=TRUE)

# primary key to merge
md_long$pk <- paste(md_long$Year,"-",md_long$variable,sep="")

# getting min for some repayment variables by year
min <- college_scorecards %>% group_by(Year) %>% summarise_each(funs(min), DEP_DEBT_MDN, FEMALE_DEBT_MDN, GRAD_DEBT_MDN, IND_DEBT_MDN, MALE_DEBT_MDN, MD_INC_DEBT_MDN, NOPELL_DEBT_MDN, NOTFIRSTGEN_DEBT_MDN, PELL_DEBT_MDN, WDRAW_DEBT_MDN)

# wide to long
min_long <- gather(min, variable, min_value, DEP_DEBT_MDN:WDRAW_DEBT_MDN, factor_key=TRUE)

# primary key to merge
min_long$pk <- paste(min_long$Year,"-",min_long$variable,sep="")

# getting max for some repayment variables by year
max <- college_scorecards %>% group_by(Year) %>% summarise_each(funs(max), DEP_DEBT_MDN, FEMALE_DEBT_MDN, GRAD_DEBT_MDN, IND_DEBT_MDN, MALE_DEBT_MDN, MD_INC_DEBT_MDN, NOPELL_DEBT_MDN, NOTFIRSTGEN_DEBT_MDN, PELL_DEBT_MDN, WDRAW_DEBT_MDN)
# wide to long
max_long <- gather(max, variable, max_value, DEP_DEBT_MDN:WDRAW_DEBT_MDN, factor_key=TRUE)
# primary key to merge
max_long$pk <- paste(max_long$Year,"-",max_long$variable,sep="")

# getting mean for some repayment variables by year
mean <- college_scorecards %>% group_by(Year) %>% summarise_each(funs(mean), DEP_DEBT_MDN, FEMALE_DEBT_MDN, GRAD_DEBT_MDN, IND_DEBT_MDN, MALE_DEBT_MDN, MD_INC_DEBT_MDN, NOPELL_DEBT_MDN, NOTFIRSTGEN_DEBT_MDN, PELL_DEBT_MDN, WDRAW_DEBT_MDN)

#wide to long
mean_long <- gather(mean, variable, mean_value, DEP_DEBT_MDN:WDRAW_DEBT_MDN, factor_key=TRUE)

# primary key to merge
mean_long$pk <- paste(mean_long$Year,"-",mean_long$variable,sep="")


# Merging data frames into one
# merge with min
repayment <- merge(x=md_long, y=min_long, by.x="pk", by.y="pk", all.x = TRUE)
# remove redundant fields
repayment <- subset(repayment, select = -c(Year.y, variable.y))

# merge with max
repayment <- merge(x=repayment, y=max_long, by.x="pk", by.y="pk", all.x = TRUE)
# remove redundant fields
repayment <- subset(repayment, select = -c(Year, variable))

# merge with mean
repayment <- merge(x=repayment, y=mean_long, by.x="pk", by.y="pk", all.x = TRUE)
# remove redundant fields
repayment <- subset(repayment, select = -c(Year, variable, pk))

names(repayment) <- c("Year", "Variable", "Maryland_Value", "Big_Ten_Min", "Big_Ten_Max", "Big_Ten_Mean")
# Sorting the Dataframe by last Variable then Year
repayment <- repayment[ order(repayment$Variable, (repayment$Year)), ]

rm(max, max_long, md_repayment, mean, mean_long, min, min_long)

# Reorder by column name
repayment <- repayment[c("Variable", "Year", "Maryland_Value", "Big_Ten_Min", "Big_Ten_Max", "Big_Ten_Mean")]

# Visualization

recent <- subset(college_scorecards, Year=="2016-17")
recent <- recent[,c("INSTNM", "Year", "group", "FEMALE_DEBT_MDN", "MALE_DEBT_MDN")]
library(ggplot2)

manual_colors <- c("#AF272F","#101820") 

vis_scatter <- ggplot(recent, aes(x=MALE_DEBT_MDN, y=FEMALE_DEBT_MDN, color=str_wrap(group,20))) + geom_point() +  labs(title = "Median Debt by Gender", subtitle = "Comparing University of MD, College Park to the Rest of the Big Ten Institutions", caption = "College Scorecard, 2016-17", x = "Median Male Debt", y = "Median Female Debt") + theme(plot.title = element_text(hjust = 0.5)) + scale_y_continuous(breaks = seq(10000, 25000, by=5000), limits=c(10000,25000))+ scale_x_continuous(breaks = seq(10000, 25000, by=5000), limits=c(10000,25000)) + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + labs(color = "Grouping")+ scale_color_manual(values = manual_colors)+ geom_point(size = 4) + theme(plot.title = element_text(hjust = 0.5)) 
vis_scatter

To see what this visualization looks like, please visit https://github.com/annlaurawalker/INFM_600/wiki/Sample-Visualizations

```
 
 
```{r message=FALSE, cache=FALSE, echo=FALSE, warning=FALSE}
 # Predictive Analytics by Himanshi Manglunia & Kalpita Raut
 #Installing packages - one time
install.packages("dplyr")
install.packages("mvnormtest")
install.packages("pwr")
install.packages("sm")

#### INFM 600 Project ####
FinalDataset <- read.csv(text=getURL("https://raw.githubusercontent.com/annlaurawalker/INFM_600/edits_descriptive/FinalDataset.csv"), header=T)
View(FinalDataset)
df4 <- na.omit(FinalDataset)
require(dplyr)
require(mvnormtest)
require(pwr)
require(sm)

#separating variables into different datasets
INSTNM <- as.factor(FinalDataset[,1])
YEAR <- as.factor(FinalDataset[,3])
C100_4			<- as.matrix(FinalDataset[,4])
C150_4          <- as.matrix(FinalDataset[,5])
D150_4          <- as.matrix(FinalDataset[,6])
COMPL_RPY_3YR_RT<- as.matrix(FinalDataset[,8])
COMPL_RPY_5YR_RT<- as.matrix(FinalDataset[,9])
DEBT_N          <- as.matrix(FinalDataset[,10])
DEP_DEBT_MDN    <- as.matrix(FinalDataset[,11])
PCTFLOAN        <- as.matrix(FinalDataset[,12])
NPT41_PUB       <- as.matrix(FinalDataset[,13])
NPT42_PUB       <- as.matrix(FinalDataset[,14])
NPT43_PUB       <- as.matrix(FinalDataset[,15])
NPT44_PUB       <- as.matrix(FinalDataset[,16])
NPT45_PUB       <- as.matrix(FinalDataset[,17])
head(INSTNM)
head(YEAR)

#create R objects for the residuals from each treatment level
resC100_4		   =lm(FinalDataset$C100_4~FinalDataset$INSTNM)$residuals
resC150_4          =lm(FinalDataset$C150_4~FinalDataset$INSTNM)$residuals
resD150_4          =lm(FinalDataset$D150_4~FinalDataset$INSTNM)$residuals
resCOMPL_RPY_3YR_RT=lm(FinalDataset$COMPL_RPY_3YR_RT~FinalDataset$INSTNM)$residuals
resCOMPL_RPY_5YR_RT=lm(FinalDataset$COMPL_RPY_5YR_RT~FinalDataset$INSTNM)$residuals
resDEBT_N          =lm(FinalDataset$DEBT_N~FinalDataset$INSTNM)$residuals
resDEP_DEBT_MDN    =lm(FinalDataset$DEP_DEBT_MDN~FinalDataset$INSTNM)$residuals
resPCTFLOAN        =lm(FinalDataset$PCTFLOAN~FinalDataset$INSTNM)$residuals
#resNPT41_PUB       =lm(FinalDataset$NPT41_PUB~FinalDataset$INSTNM)$residuals
#resNPT42_PUB       =lm(FinalDataset$NPT42_PUB~FinalDataset$INSTNM)$residuals
#resNPT43_PUB       =lm(FinalDataset$NPT43_PUB~FinalDataset$INSTNM)$residuals
#resNPT44_PUB       =lm(FinalDataset$NPT44_PUB~FinalDataset$INSTNM)$residuals
#resNPT45_PUB       =lm(FinalDataset$NPT45_PUB~FinalDataset$INSTNM)$residuals

#checking for normality using qqplots
qqnorm(lm(FinalDataset$C100_4~FinalDataset$INSTNM)$residuals, main="resC100_4		   ", col=4)
qqline(lm(FinalDataset$C100_4~FinalDataset$INSTNM)$residuals, lwd=2,col='gray86')

qqnorm(lm(FinalDataset$C150_4~FinalDataset$INSTNM)$residuals, main="resC150_4          ", col=4)
qqline(lm(FinalDataset$C150_4~FinalDataset$INSTNM)$residuals, lwd=2,col='gray86')

qqnorm(lm(FinalDataset$D150_4~FinalDataset$INSTNM)$residuals, main="resD150_4          ", col=4)
qqline(lm(FinalDataset$D150_4~FinalDataset$INSTNM)$residuals, lwd=2,col='gray86')

qqnorm(lm(FinalDataset$COMPL_RPY_3YR_RT~FinalDataset$INSTNM)$residuals, main="resCOMPL_RPY_3YR_RT", col=4)
qqline(lm(FinalDataset$COMPL_RPY_3YR_RT~FinalDataset$INSTNM)$residuals, lwd=2,col='gray86')

qqnorm(lm(FinalDataset$COMPL_RPY_5YR_RT~FinalDataset$INSTNM)$residuals, main="resCOMPL_RPY_5YR_RT", col=4)
qqline(lm(FinalDataset$COMPL_RPY_5YR_RT~FinalDataset$INSTNM)$residuals, lwd=2,col='gray86')

qqnorm(lm(FinalDataset$DEBT_N~FinalDataset$INSTNM)$residuals, main="resDEBT_N          ", col=4)
qqline(lm(FinalDataset$DEBT_N~FinalDataset$INSTNM)$residuals, lwd=2,col='gray86')

qqnorm(lm(FinalDataset$DEP_DEBT_MDN~FinalDataset$INSTNM)$residuals, main="resDEP_DEBT_MDN    ", col=4)
qqline(lm(FinalDataset$DEP_DEBT_MDN~FinalDataset$INSTNM)$residuals, lwd=2,col='gray86')

qqnorm(lm(FinalDataset$PCTFLOAN~FinalDataset$INSTNM)$residuals, main="resPCTFLOAN        ", col=4)
qqline(lm(FinalDataset$PCTFLOAN~FinalDataset$INSTNM)$residuals, lwd=2,col='gray86')

#qqnorm(lm(FinalDataset$NPT41_PUB~FinalDataset$INSTNM)$residuals, main="resNPT41_PUB       ", col=4)
#qqline(lm(FinalDataset$NPT41_PUB~FinalDataset$INSTNM)$residuals, lwd=2,col='gray86')
#
#qqnorm(lm(FinalDataset$NPT42_PUB~FinalDataset$INSTNM)$residuals, main="resNPT42_PUB       ", col=4)
#qqline(lm(FinalDataset$NPT42_PUB~FinalDataset$INSTNM)$residuals, lwd=2,col='gray86')
#
#qqnorm(lm(FinalDataset$NPT43_PUB~FinalDataset$INSTNM)$residuals, main="resNPT43_PUB       ", col=4)
#qqline(lm(FinalDataset$NPT43_PUB~FinalDataset$INSTNM)$residuals, lwd=2,col='gray86')
#
#qqnorm(lm(FinalDataset$NPT44_PUB~FinalDataset$INSTNM)$residuals, main="resNPT44_PUB       ", col=4)
#qqline(lm(FinalDataset$NPT44_PUB~FinalDataset$INSTNM)$residuals, lwd=2,col='gray86')
#
#qqnorm(lm(FinalDataset$NPT45_PUB~FinalDataset$INSTNM)$residuals, main="resNPT45_PUB       ", col=4)
#qqline(lm(FinalDataset$NPT45_PUB~FinalDataset$INSTNM)$residuals, lwd=2,col='gray86')


#manova test
x <- manova(cbind(
  FinalDataset$C100_4			 ,
  FinalDataset$C150_4          ,
  FinalDataset$D150_4          ,
  FinalDataset$COMPL_RPY_3YR_RT,
  FinalDataset$COMPL_RPY_5YR_RT,
  FinalDataset$DEBT_N          ,
  FinalDataset$DEP_DEBT_MDN    ,
  FinalDataset$PCTFLOAN        ,
  FinalDataset$NPT41_PUB       ,
  FinalDataset$NPT42_PUB       ,
  FinalDataset$NPT43_PUB       ,
  FinalDataset$NPT44_PUB       ,
  FinalDataset$NPT45_PUB       
) ~ FinalDataset$INSTNM, data = FinalDataset)

#running wilks test
summary(x,test="Wilks")

#difference between the response vars
summary.aov(x)
```
# Visualizations done by Laura Walker
college_scorecards <-read.csv(text=getURL("https://raw.githubusercontent.com/annlaurawalker/INFM_600/edits_descriptive/FinalDataset.csv"), header=T)

# constructing a data frame of completion for non-white students
completion_rates <- college_scorecards[,c("INSTNM","Year",  "D150_4_2MOR", "D150_4_AIAN", "D150_4_ASIAN", "D150_4_BLACK", "D150_4_HISP", "D150_4_NHPI", "D150_4_NRA", "D150_4_UNKN")]

# making data wide to long
completion_rates_long <- gather(completion_rates, variable, value, D150_4_2MOR:D150_4_UNKN, factor_key=TRUE)

# classifying races into Underrepresented minority groups. 
completion_rates_long$URM <- ifelse(completion_rates_long$variable== "D150_4_UNKN", "Unknown", ifelse(completion_rates_long$variable== "D150_4_NRA", "Foreign", ifelse(completion_rates_long$variable== "D150_4_ASIAN" |completion_rates_long$variable== "D150_4_2MOR", "Other Minority", "Under-Represented Minority")))


# creating a new field for a shortened year
completion_rates_long$Year_Short <- ifelse(completion_rates_long$Year== "2016-17", 2017, ifelse(completion_rates_long$Year== "2015-16", 2016, ifelse(completion_rates_long$Year== "2014-15", "2015", ifelse(completion_rates_long$Year== "2013-14", 2014, 2013))))

vis_stacked <-ggplot(completion_rates_long,   aes(x=Year_Short, y=value, fill=str_wrap(URM, 20))) + geom_bar(stat="identity", position = "fill") + scale_y_continuous(labels = percent_format()) + theme_bw() + labs(title = "Non-White Completion Breakdown", subtitle = "", caption = "College Scorecards, 2012-2013 to 2016-2017", x = "Year", y = "Total") + theme(panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + facet_wrap(~INSTNM, labeller = label_wrap_gen(multi_line = TRUE), scales="free", ncol=3) +scale_fill_brewer(palette="Set3") 

To see what this visualization looks like, please visit https://github.com/annlaurawalker/INFM_600/wiki/Sample-Visualizations
```
